---
title: "Day 1 Interactive Session 2"
author: "Jake Eisaguirre"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

### Logs and Exponents in R

Some examples of using `log()`function and `exp()` function in R

```{r}
# Examples of Logarithms

log(4)

#Example of exponents

exp(5)

log(exp(1))

```


### Creating Sequences of values

```{r}
# A sequence from 1 to 20, by 1 

ex_1 <- seq(from = 1, to = 20, by = 1)

# Vector from 0 to 40 by increments of 0.2

ex_2 <- seq(from = 0, to = 40, by = 0.2)

# Vector from 1 to 5000 increments of 10

ex_3 <- seq(from = 1, to = 5000, by = 10)

```

### Create a function fro logistic growth

Given the carrying capacity, initial populatio, the growth rate, ad time, use the logistic growth model to estimate the population at that time

```{r}
#Logistic growth function

pop_logistic <- function(capacity, init_pop, rate, time_yr) {
  
  capacity/ (1 + ((capacity - init_pop) / init_pop) * exp(-rate * time_yr))
  
}

pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = 2.4)


```

### Try finding population over a sequence

```{r}

time_vec <- seq(from = 0, to = 15, by = 0.5)



```

Now lets estimate the population over that range of times, given capacity= 2580, initial population = 230, rate = 0.32

```{r}

chipmunk_pop <- pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = time_vec)


```

### Create a data frame and plot chipmunk population over time

```{r}

chipmunk_df <- data.frame(time_vec, chipmunk_pop)

chipmunk_df


```


### Create a bare min ggplot graph:

```{r}

ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) + 
  geom_point() + 
  labs(x = "Time (years)", y = "Chipmunk population (ind)", title = "Inyo NF chipmunks")

```

